---
output: pdf_document
---
In my R code below, I use the following variable names:

  - $\sigma_{D}$ is represented by sigmaD, which is the standard deviation calculated from (b)
  - $\sigma_{\bar{D}}$ , the standard error, is represented by sigma_barD 
  - $\mu_{\bar{D}}$ , the sample distribution mean, is represented by mu_barD

```{r}
#storing population standard deviation
(sigmaD = ((pi/4)-(pi/4)**2)**0.5)

#using standard deviation to caculate standard error
(sigma_barD = sigmaD/(100**0.5))

#storing the sample distribution mean
(mu_barD = pi/4)
```

```{r}
#calculating the probability of sample mean greater than 3/4
(1-pnorm(3/4, mean = mu_barD, sd=sigma_barD))
```
From this output, we have that the $P(\bar{D}>\dfrac{3}{4})\approx\boxed{0.8057}$

(e) Simulating a single draw can be done using runif() which creates random samples for a uniformly distributed random variable within the minimum and maximum bounds used to define the distribution. The first 3 arguments of the runif() function are the number of samples n, the min bound of the distribution, and the max bound of the distribution.

As discussed in (a), $X_i$ and $Y_i$ have uniform distribution in the region [-1, 1], so the arguments for runif() can be set as follows:

 - n=100
 - min = -1
 - max = 1

Given the independence of $X_i$ and $Y_i$, runif() is ran separately to create the sample results stored in vectors x and y:
```{r}
x = runif(100, min = -1, max = 1)
y = runif(100, min = -1, max = 1)
```
Next, I create a function called D_i for calculating $D_i$, which takes 2 arguments that represent $X_i$ and $Y_i$.  Then I store the results for D_i operating on the vectors x and y in the results vector d
```{r}
D_i = function(x,y) {
  ifelse((x**2+y**2)<1, 1, 0)
}
d = D_i(x,y)
```

Finally, I plot my samples (x,y) in the x-y plane where the data points for $D_i$ = 1 (which corresponds to d=1) are color-coded red, and data points for $D_i$ = 1 are black: 
```{r}
plot(x,y, col=d+1, asp = 1, main = 'Distribution of X, Y and D')
legend(-2, 1, legend=c("d=0", "d=1"),
       col=c("black", "red"), cex=0.8, pch = 1:1)
```

From this graph, we can see that for n=100 random samples, the complete distribution of (x,y) rougly resembles a square that spans from -1 to 1 for x and from -1 to 1 for y. The red points that correspond to d = 1 roughly form the shape of the unit circle.  As expected, the points of the sample lie within the square bounds and the points for d=1 lie within the circular bounds that correspond to the figure I created for part (a).


(f) The sample average, $\bar{D}$ can be computed using the mean() function as follows:
```{r}
#sample average
(sample_mean = mean(d))

#expected sample average from (a)
(pi/4)
```
The two outputs above show that the average of the sample and the expected mean calculated from part (a) $\dfrac{\pi}{4}\approx0.7853982$ , are quite close, but not exactly equal to each other.  This is expected, since the sample distribution for $\bar{D}$ has non-zero variance. We would expect the measurement of $\bar{D}$ for a sample to deviate from the expected mean and also to be different from sample to sample.  

(g) To generate 10,000 samples, we can use the replicate() function in R. First, we will need to define a function, D_bar, which will accomplish the following:
  - Create X and Y samples of size n. 
  - Calculated the corresponding value of $D_i$ for every $(X_i,Y_i)$ using the previously defined function D_i.
  - Calculate and return the sample mean $\bar{D}$ as the output.
  
```{r}
D_bar = function(n){
  x_j = runif(n, -1, 1)
  y_j = runif(n, -1, 1)
  
  d_j = D_i(x_j,y_j)
  return(mean(d_j))
}
```

Next, I will set the sample size and replicate the simulation function D_bar 10,000 times:
```{r}
#set sample size
n = 100

#store sample means for 10,000 draws in vector
sample_means_D = replicate(10000,  D_bar(n))
```

Lastly, I plot a histogram for the results of the simulation, which are 10,000 values of $\bar{D}$ stored in the vector sample_means_D:
```{r}
# plot sample means as histogram
hist(sample_means_D, breaks=40, xlab = 'Sample Mean', 
     ylab = 'Frequency', main = 'Sample Distribution for n=100')
```

From the histogram above, we see that the sample distribution for $\bar{D}$ has the rougly the shape of a normal distribution.

(h) The standard deviation of sample means can be calculated using the sd() function as follows:
```{r}
sd(sample_means_D)
```
The output here is also very close in comparison to the result from (c) 0.0410546.  This result aligns with our expectation from the CLT, which states that for a sufficiently large sample, sample distribution can be approximated with a normal distribution that has standard deviation equal to the standard error found in (c)

(j) To calculate the fraction of sample averages that are larger than 3/4, I use length() function which counts the number of elements. I can then slice sample_means_D to pick out a subset of numbers that are greater than 3/4, then divide the length() of this subset by the length of the entire vector() sample_means_D: 
```{r}
length(sample_means_D[sample_means_D>0.75])/length(sample_means_D)
```

This output from the simulation of 10,000 draws is very close to answer from (d) $P(\bar{D}>\dfrac{3}{4})\approx0.806$, but the two values are also not exactly equal.

From both the CLT and the histogram shown in (g), we know that the normal distribution is only an approximation for the sample distribution of $\bar{D}$ , but there will be some error. Therefore we should expect some deviation of the actual observed fraction of samples where $\bar{D}>\dfrac{3}{4}$ compared to the calculated probability that $\bar{D}>\dfrac{3}{4}$ using the normal distribution. 
